|

### 2022-07-25 manuscript.Rmd
add GitHub repo link
missing package info

We show an example of incorporating these three basic rules by using the Palmer Penguins data <!--Mine will cite this-->. 
We visualize the relationship between flipper length and bill length of penguins and color the data points differently for each species in Figure \ref{fig:penguins-basic}.

@@

The `colorblindr` package [@R-colorblindr] provides a set of functions that can be useful in teaching and practising color blindness accessibility. 
For instance, `cvd_grid()` function provides color-deficiency simulations of a given plot. 
In the code chunk below the plot is named as `fig`. 
The code creates a grid of four plots where each plot shows a different color vision deficiency.
This grid allows those without any color vision deficiencies experience what data visualizations would look like to a sighted person that does have color blindness.

>>>>

We show an example of incorporating these three basic rules by using the Palmer Penguins data [@R-palmerpenguins]. 
We visualize the relationship between flipper length and bill length of penguins and color the data points differently for each species in Figure \ref{fig:penguins-basic}.

@@

The `colorblindr` package [@R-colorblindr] provides a set of functions that can be useful in teaching and practising color blindness accessibility. 
For instance, `colorblindr::cvd_grid()` function provides color-deficiency simulations of a given plot. 
In the code chunk below the plot is named as `fig`. 
The code creates a grid of four plots where each plot shows a different color vision deficiency.
This grid allows those without any color vision deficiencies experience what data visualizations would look like to a sighted person that does have color blindness.
